\documentclass[12pt]{article}
\title{\textbf{Hanabi Testing Plan}}
\author{Mels Kolozyan\\
		Xudong Li\\
		Xufeng Lin\\
		Evan Semenoff\\
		Tiandu Xie\\
		}
\date{}
\begin{document}

\pagenumbering{gobble}
\maketitle
\newpage	
\pagenumbering{arabic}

\newpage

\part{Introduction}

This document outlines the testing plan which will be used during the implementation
phase.  It is split into three parts, the first will cover end-to-end tests, which are
directly related to use cases found in the requirements documentation.  Next, the
integration testing will be covered, this will reflect the architectural decisions made
in the design document.  Finally, unit testing will address the testing of the classes
and methods which were outline in the design document.

\part{End-To-End Testing}

Each of the following tests reflects a specific use-case as seen in the requirements
documentation (page 15).  Each use-case will have two cases which will be covered: cases
which cause the use-case to happen, and cases which won't.  These will be denoted as positive
(+) and negative (-) cases.

\section{Create Table}

\begin{itemize}

\item[+] Well Formed Input: The user has given a valid string to create a game with
\item[+] Can Be Made: The game can be made.
\item[+] Auto Join: Given that both of the previous conditions have been met, the
user is joined into the game they created.

\item[-] Malformed Input: The user has given an invalid string.
\item[-] Connection Error: A connection to the server cannot be established.
\item[-] Game Can't Be Made: The server is unable to create the game.

\end{itemize}

\section{Play Card}

\begin{itemize}

\item[+] Was Valid: This causes two unique things to happen
\begin{itemize}
\item The card is played
\item The score is incremented
\end{itemize}
\item[+] Wasn't Valid: This causes two unique things to happen
\begin{itemize}
\item The card is put into the discards
\item A fuse is removed
\end{itemize}
Both of these actions cause a set of four actions that they share:
\begin{itemize}
\item A new card is dealt
\item The players turn ends
\item The card pile is decremented
\item The timer is reset
\end{itemize}
\end{itemize}

\section{Hint}

\begin{itemize}
\item [+] Hint Given: This causes a hint to be given to another player, this causes four
things to happen
\begin{itemize}
\item The turn is changed
\item A hint is sent
\item The number of hint tokens goes down
\item The timer is reset
\end{itemize}

\item [-] No Tokens: This stops the player from giving a hint (by making the
option unavailable)

\end{itemize}

\section{Discard}

\begin{itemize}
\item[+] Discard: This is the basic discard use-case, it causes many things to happen.
\begin{itemize}
\item The tokens go up
\item A new card is drawn
\item A card is appended to the discards
\item The number of cards left is decremented
\item The turn ends
\item The timer is reset
\end{itemize}

\item [-] Tokens Full: This stops the player from discarding (by making the action
into a null action)

\end{itemize}

\section{View Discards}

\begin{itemize}
\item[+] View Discards: The discards are drawn as an overlay on-top of the screen.

\item[-] Drawn Improperly: There are a few cases to consider
\begin{itemize}
\item Not drawn in the correct order
\item Not drawing the correct cards
\item Not drawing the discards (drawing some other cards)
\end{itemize}

\end{itemize}

\section{Personal Notes}

\begin{itemize}
\item[+] Personal Notes: Drawn as an overlay on top of the screen
\item[+] Cyclical hints: The hints cycle properly when clicking on them

\item[-] Drawn Improperly: The hint graphics don't reflect their state
\item[-] Broken Button: The button doesn't work

\end{itemize}

\section{Start AI}

\begin{itemize}
\item[+] AI Starts: The AI takes over the the game
\item[-] AI Won't Start: The AI won't start
\item[-] AI Won't Play: The AI won't make moves

\end{itemize}

\section{End AI}

\begin{itemize}
\item[+] AI Stops: The AI lets the human player play again
\item[-] AI Won't Stop: The AI won't stop playing
\end{itemize}

\section{Exit}
\begin{itemize}


\item[+] Exit: The connection is severed and the player returns to the main menu
\item[-] Can't Exit: The user can't exit the game without closing the window, or the
exit button doesn't return them to the main menu.
\end{itemize}
\section{Join Table}
\begin{itemize}
\item[+] The player can successfully join a table given he meets these preconditions:
\begin{itemize}
\item The game is not full
\item The input is well formed
\item The game exists
\end{itemize}
\item[-] Malformed Input: The string entered is not valid
\item[-] Connection Error: Cannot connect to the server
\item[-] Game Doesn't Exist: No game exists with those credentials
\item[-] Game is Full: There is no more room at the given table
\end{itemize}




\newpage
\part{Integration Testing}
\setcounter{section}{0}
The integration tests were developed by breaking down the cases of the end-to-end tests, and
outlining how they fit into the architecture.  For brevity, the symbols C, M, V, and S will
refer to the controller, the model, the view, and the server, respectively.  This phase will
outline how the code fits together and will allow us to verify that the modules fit together
during the scaffolding phase.





\section{Create Table}

\begin{itemize}

\item[+] Well Formed Input: C $\rightarrow$ C \newline
The controller takes in a valid string, and creates a game
\item[+] Can Be Made: S $\rightarrow$ C $\rightarrow$ M $\rightarrow$ V \newline
The controller receives verification from the server, a GameState is instantiated,
and the view begins to draw the table.
\item[+] Auto Join: C $\rightarrow$ S \newline
The controller joins the game which was created.

\item[-] Malformed Input: C $\rightarrow$ V \newline
The controller detects an invalid string, a window is drawn in the view to inform the user
\item[-] Connection Error: C $\rightarrow$ M $\rightarrow$ V \newline
The controller cannot connect to the server, this is reflected in the view via a pop-up
\item[-] Game Can't Be Made: C $\rightarrow$ M $\rightarrow$ V \newline
For some reason, the game cannot be made.  The user is informed via pop-up

\end{itemize}

\section{Play Card}

\begin{itemize}

\item[+] Was Valid: C $\rightarrow$ S $\rightarrow$ C $\rightarrow$ M $\rightarrow$ V \newline
The controller sends a valid move to the server, which returns a JSON packet.  The packet
is parsed, and the game state is updated, which is reflected in the view.
\item[+] Wasn't Valid: C $\rightarrow$ S $\rightarrow$ C $\rightarrow$ V \newline
Exactly the same as was valid, but different things are updated.
\item[+] Null Case: C $\rightarrow$ M $\rightarrow$ V $\rightarrow$ M $\rightarrow$ V \newline
The user tries to play a move that isn't valid (perhaps attempting to discard when the tokens are
full).  The controller determines the move is invalid and reverts the client state to before the
move was attempted.
\end{itemize}

\section{Hint}

\begin{itemize}
\item [+] Valid Hint:  C $\rightarrow$ M $\rightarrow$ V $\rightarrow$ C $\rightarrow$ M 
$\rightarrow$ V $\rightarrow$ C $\rightarrow$ S \newline
The user selects the first card, and then creates a valid hint packet after enough
cards are selected.

\item [+] Invalid Hint: C $\rightarrow$ M $\rightarrow$ V $\rightarrow$ C $\rightarrow$ M 
$\rightarrow$ V \newline
The user selects a card that conflicts with the other selection while giving a hint. The
other card is deselected and nothing is sent to the server.

\item [+] Hint Received: S $\rightarrow$ C $\rightarrow$ M $\rightarrow$ V \newline
A player at the table receives a hint.  The model is updated, and the view plays a short
animation to convey this information.

\item [-] No Tokens: M $\rightarrow$ V
If no tokens are available, this is reflected in the view.

\end{itemize}

\section{Discard}

\begin{itemize}
\item[+] Discard: C $\rightarrow$ S $\rightarrow$ C $\rightarrow$ M $\rightarrow$ V \newline
Whenever a discard happens, the controller sends a message to the server indicating
this, once the message is received, the model is updated (discards are appended)
and the view is updated.

\item [-] Tokens Full: M $\rightarrow$ V \newline
If the token counter is full, this is reflected in the view.
\end{itemize}

\section{View Discards}

\begin{itemize}
\item[+] View Discards: C $\rightarrow$ M $\rightarrow$ V \newline
The controller detects that the user has opened the discards menu, the client state
is updated, and the view reflects this change.

\end{itemize}

\section{Personal Notes}

\begin{itemize}
\item[+] Personal Notes: C $\rightarrow$ M $\rightarrow$ V \newline
The user clicks on the notes menu, and the notes about the cards are updated in 
the client state, this is reflected in the view.

\end{itemize}

\section{Start AI}

\begin{itemize}
\item[+] AI Starts: C $\rightarrow$ M $\rightarrow$ V \newline
The user requests that the AI plays for them, this creates a new instance of the AI. The button to start the AI is changed to a button that says "Stop AI".

\end{itemize}

\section{End AI}

\begin{itemize}
\item[+] AI Stops: C $\rightarrow$ M $\rightarrow$ V \newline
The user requests to get control back.  This is just like the start AI but in reverse.
\end{itemize}

\section{Exit}
\begin{itemize}


\item[+] Exit: C $\rightarrow$ M $\rightarrow$ V \newline
The user leaves the game, the model deletes the game state, and the game is set back
to the main menu.

\end{itemize}
\section{Join Table}
\begin{itemize}
\item[+] Join Table: C $\rightarrow$ S $\rightarrow$ C $\rightarrow$ V \newline
The controller requests to join a game, the server responds accordingly, and the
controller instantiates a game state (which is immediately reflected in the view).
\end{itemize}

\part{Unit Testing}
\setcounter{section}{0}
\section{GameState}
\begin{description}
	\item[appendDiscard] Adds a new discarded card to the linked list of discards.
	\begin{itemize}
		\item Linked list length Incremented: The linked list of discards should increment by one due to append.
		\item The Last Element: The last element in the linked list should be the recently discarded card.
	\end{itemize}
	\item[updateCardsOnTable] Updates cards played on the table after a legal card is played.
	\begin{itemize}
		\item New Card in Array: The played card can be found in the array of cards on table.
		\item Correct Index: The played card is in the correct index or position.
    \end{itemize}
    \item[updatePlayerHand] Updates cards in a player's hand in the array of players.
	\begin{itemize}
		\item Card Played and Replaced: The card that is played gets replaced by a new card (expect the last round).
		\item New Card in Hand: A new card is drawn by the player who played a card.
	\end{itemize}
\end{description}

\section{ClientState}
\begin{description}
	\item[selectCard] Set the card at the given index of the array to Selected
	\begin{itemize}
		\item Correct Player: The player should be in the given player index of the player array.
		\item Correct Card: The card should be in the given card index of the player's hand array.
		\item Set Selected Cards: The Selected attributes of the selected cards should be set to True.
	\end{itemize}
	\item[ToggleMenu] Toggle the boolean value at the index of MenusOpen dictionary.
	\begin{itemize}
		\item Test the Toggle: the boolean at the MenusOpen index of the dictionary shall be toggled (set to True if was False, set to False otherwise)
    \end{itemize}
\end{description}

\section{Player}
\begin{description}
	\item[updateHand] Updates cards in the player's hand in the array of players.
	\begin{itemize}
		\item Card Played and Replaced: The card that is played gets replaced by a new card (except the last round).
		\item New Card in Hand: A new card is drawn by the player who played a card.		
	\end{itemize}
\end{description}

\section{Controller}
\begin{description}
	\item[RecieveServerData] responsible for getting the data off of the buffer
	\begin{itemize}
		\item + JSON exists: check that a JSON packet is in the buffered reader. This method is called only when the socket receives a reply from the server, so there has to be an item stored on the buffer.
	\end{itemize}
	\item[ParseJSON] should be taking in a json message and outputting an appropriate java construct
	\begin{itemize}
		\item + Event Map is correct: check that the provided event map is of the proper format (required by the server). 
	\end{itemize}
	
	\item[EvalEvent] Most of the logic of the controller is handled by this function, so there are a lot of test cases here to assure non-faulty communication with the other modules of the program. 
	\begin{itemize}
    \item +Player joined
    \begin{itemize}
    \item Send dialog update to let the player know about the new player joining
    \end{itemize}

		                
		\item +Player left
		\begin{itemize}
		    \item Send dialog update to let the player know about a player leaving the game before a game starts
		\end{itemize}
		                
		\item +Game Starts: a message is received about the start of the game which instantiates the game and the main program itself
		\begin{itemize}
		    \item instanties the rest of the game state (fields like player cards and turn)
		    \item the main loop begins 
		    \item rtthread for the turn timer
		\end{itemize}
		\item +Your Turn: signals the first players about the start of their turn
		\begin{itemize}
		    \item the local turn variable (in game state) set to yourself
		\end{itemize}
		\item +Invalid Action: received when a sent action was determined to be invalid
		\begin{itemize}
		    \item As the GUI does not allow for illegal actions to be sent in the first place, this occurrence throws an exception
		\end{itemize}
		\item +Game Cancelled: received when a player leaves the game early
		\begin{itemize}
		    \item Message(dialog): lets the player know why the game was stopped, test for the dialog box popping up
		    \item return to the main menu (test if the main menu was redrawn)
		\end{itemize}
		\item +Discarded(notice): the server sends this notice to let them know about a discard that another player did. It also send the information on the new card and a lot of things in the game state must be updated.
		\begin{itemize}
		    \item AppendDiscards: test if the card was added to the discard pile
		    \item UpdatePlayer: test if the new drawn card is now part of the player's hand
		    \item Inc Turn: make sure the turn is given to the next player
		    \item DecCards: verify that the new cards count is decremented
		    \item Tokens Inc: discarded card should increment the amount of tokens
		    \item NewCardDrawn: Test if the new card is properly drawn on the game screen
		    \item TimeReset: the timer is reset for the next player
		    
		\end{itemize}
		\item +Accepted(reply): the reply is sent to the player who made the discard
		\begin{itemize}
		    \item AppendDiscards: test if the card was added to the discard pile
		    \item Inc Turn: make sure the turn is given to the next player
		    \item DecCards: verify that the new cards count is decremented
		    \item Tokens Inc: discarded card should increment the amount of tokens
		    \item TimeReset: the timer is reset for the next player
		\end{itemize}
		
		\item +Played(notice): the server sends this notice to other players, and tell them what new card the player drew 
			\begin{itemize}
		    	\item UpdatePlayer: test if the new drawn card is now part of the player's hand
		    	\item IncTurn: make sure the turn is given to the next player
		    	\item DecCards: verify that the new cards count is decremented
		    	\item TimeReset: the timer is reset for the next player
			\item ScoreUp(If it is a legal play): make sure the score is correctly added
			\item UpdateTable(If it is a legal play): verify that the played card is now placed on the correct position of the table
			\item DecFuses(If it is NOT a legal play): the fuses should be decreased by 1
    			\end{itemize}

        \item +Built(reply): the reply is sent to the player who played card if the card is legal
			\begin{itemize}
		    	\item IncTurn: make sure the turn is given to the next player
		    	\item DecCards: verify that the new cards count is decremented
		    	\item TimeReset: the timer is reset for the next player
			\item ScoreUp: make sure the score is correctly added
			\item UpdateTable: verify that the played card is now placed on the correct position of the table
			\item TokenInc(If the card rank is equal to 5): successfully play a rank 5 card should increase the amount of tokens
    			\end{itemize}
		\item +Burned(reply): the reply is sent to the player who played card if the card is NOT legal
			\begin{itemize}
		    	\item IncTurn: make sure the turn is given to the next player
		    	\item DecCards: verify that the new cards count is decremented
		    	\item TimeReset: the timer is reset for the next player
			\item DecFuses: the fuses should be decreased by 1 if it is an illegal play
			\item AppendDiscards: test if the card was added to the discard pile
    			\end{itemize}
		\item +GameEnds(notice): the server will notify all players if certain conditions are met
			\begin{itemize}
		    	\item ShowGameOver: a dialog that contains game over information should be poped up
		    	\item CloseConnection: connection to each player should be closed and game is destroyed
		    	\item GoToMainMenu: users' screen should atomatically jump to main menu after connection is closed
			\item SetGameStateNull: game state model should be set to null after previous game is destroyed
    			\end{itemize}
		\item +Inform(notice to informed player):
			\begin{itemize}
		    	\item IncTurn: make sure the turn is given to the next player
		    	\item TimeReset: the timer is reset for the next player
			\item DecTokens: verify the amount of tokens is decreased after a hint is given
			\item UpdateHands: make sure the player's hands is updated accroding to the hint
    			\end{itemize}
		\item +Inform(notice to other players):
			\begin{itemize}
		    	\item IncTurn: make sure the turn is given to the next player
		    	\item TimeReset: the timer is reset for the next player
			\item DecTokens: verify the amount of tokens is decreased after a hint is given
			\item Animation: an information should be given that indicates a hint is given by a player to another
    			\end{itemize}
	\end{itemize}
	
	\item[SendMove] responsible for sending data to the server
	\begin{itemize}
		\item + server responsed: this method will be test together with receive server data, it will check if there is a reply message sent by server after sendMove method is called. Server has to reply something after it sends a JSON package
	\end{itemize}
	\item[PackStream] convert a move message from the player's action into a JSON object which can be read by server
	\begin{itemize}
		\item + Right move is constructed: check the information that output object contains, a JSON object should be created with correct action, correct player, and correct card based on the user's input
	\end{itemize}
	\item[handleInputEvent] listens to mouse events and does functions based on different requests
	\begin{itemize}
		\item + Verify Mouse Event: several mock situation will be given to verify all five mouse events (mouseOver, mouseOut, mousePressed, mouseDraged, mouseReleased) are successfully handled
	\end{itemize}

	
	
\end{description}

\section{AI}
\begin{description}
	\item[devourStack] Move through each move one by one from the stack of moves to create a statistical model for the AI.
	\begin{itemize}
		\item + Given Stack Get CPT: The conditional probability table (CPT) is created with correct dimensions and values. 
	\end{itemize}
	\item[updateCPT] Update the conditional probability tables (CPT) of the AI.
	\begin{itemize}
		\item + Sum of all probabilities: the sum of probabilities from the CPT shall be equal to one.
    \end{itemize}
\end{description}


\part{Summary}

This testing plan was designed to help aid in construction of the game, and guide the
coding phase of the project.  The end-to-end tests cover the actual usage of the game
client, and come directly from the requirements documentation.  The integration tests
break down the various cases addressed in the end-to-end tests, and map them to corresponding
parts in the architecture.  Finally, the unit tests address the individual modules (classes
and methods) and allow us to confirm correct implementation.

\end{document}
